% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Arber Shabhasa}

\basicInfo{
  \email{ashabhasa@gmail.com} \textperiodcentered\
  \phone{(+39) 328-305-6933} \textperiodcentered\
  \linkedin[ashabhasa]{https://www.linkedin.com/in/ashabhasa} \textperiodcentered\
  \github[ashabhasa]{https://www.github.com/ashabhasa}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University degli Studi di Bologna}, Bologna, Italy}{2003 -- 2007}
\textit{B.S.} in Computer Engineering

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Sibill} Milan, Italy}{Aug. 2022 -- Present}
\role{Senior Enigeneer}{}
Brief introduction: At Sibill we're building the future of cashflow and invoice management for small and medium enterprises (SME).
Leveraging cutting edge tech we're offering SMEs a comprehensive tool that automates most of the daunting tasks that otherwise would have to be handled manually.
The product offers features that are invaluable for the CFOs like the Cashflow where you can see in real time the situation of your finances and keep them organized.
We also offer a bookkeeping solution that allows a very strait forward way to issue electronic invoices.
My role as an engineer is to help design build and test the product.

\datedsubsection{\textbf{Yoox Net-A-Porter Group.} Bologna, Italy}{Feb. 2017 -- Aug. 2022}
\role{Senior Software Developer}{}
Brief introduction: Design implement and test the order management system for an e-commerce site.
Using different technologies like .Net (C\#) and Java (Scala/Java) we deliver the software platform upon which the whole e-commerce activities of Ynap group are founded.
I’ve had to tackle different problems during this experience like concurrency, distributed systems design, refactoring of legacy codebases etc.
Currently I’m using functional programming to help integrate different systems.

\datedsubsection{\textbf{Yoox Group}}{Nov. 2013 -- Feb. 2017}
\role{Software Developer}{Contractor}
Brief introduction: Responsible for designing and implementing the backend platform for the group.
\begin{itemize}
  \item Designed/Implemented the cart api.
  \item Designed/Implemented the exchange api.
  \item Refactored legacy apis.
\end{itemize}

\datedsubsection{\textbf{Cineca/Kion}}{Jan. 2011 -- Nov. 2013}
\role{Software Developer}{Contractor}
Brief introduction:
I was part of a team that developed the governance platform that is used by most of the Italian universities (U-Gov).
The software handles different aspects of the life of the university's administration. It offers different tools of analysis and reporting and supports the strategic and operative planning of the different universities.
The development was done on the Java platform using Oracle as the database solution.

\datedsubsection{\textbf{Apex net}}{Jan. 2009 -- Dec. 2011}
\role{Software Developer}{}
Brief introduction: I was part of a team that developed different web based/mobile applications.
The applications helped Credit Institutions to perform and then assess real estate surveys.
As this was a small team I had to perform different tasks ranging from requirements gathering to analysis of the requirements, implementation, testing and deployment of the application.
We used different tools to implement the applications, web based applications were developed using the .Net platform whereas mobile applications were developed using iOS and Android.

\begin{itemize}
  \item Designed/Implemented new applications for iOS
  \item Implemented web based apps using .Net
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Test Driven Development
  \item Refactoring
  \item Programming Languages: Scala, Java, C\#, Elixir
  \item Databases: PostgreSQL/SqlServer/Oracle/Mongo
\end{itemize}

\section{\faHeartO\ Interests}
\begin{itemize}[parsep=0.5ex]
  \item Functional programming
  \item Distributed systems
  \item Reading
  \item Running
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Languages: English - Fluent, Italian - Fluent, Albanian - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
